Backpropagating Gravitational wave events

### 2022-04-20 src/ms.tex
Remove some comments
update

\wf{Re-writing the methods section with a new viewpoint, gonna try to eventually merge the content.}

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_reprojection.pdf}
\caption{Reprojecting the posterior in evolutionary parameter space of GW150914 to observable space.
The blue contour is the posterior reprojected using the samples in the evolutionary parameter space.
The orange contour is the posterior samples from LVK that have corresponding samples in the evolutionary parameter space.
The green contour is the posterior plotted using all of LVK posterior samples.
}
\label{fig:GW150914_reprojection}
\end{figure}

We can see the reprojected posterior agrees very well with the original posterior in fig.\ref{fig:GW150914_reprojection}.
\kw{Qoute the KL divergence.}

@@

The most important point in this paper is illustrated in figure \ref{fig:GW150914_m1_m2_alpha}.
We can see the posterior samples in $M_1-M_2$ space are spatially correlated with $\alpha$,
this means if we fixed the value of $\alpha$ instead of allowing it to jointly vary with all other parameters,
we would miss the samples that do not match the chosen value of $\alpha$.
By folding in the hyper-parameters into the root-finding algorithm,
we can capture the correlation between 
\kw{Dartboard comparsion} Comparing our result with 
\kw{Add figure showing hyper-parameters are important to recovering the progenitor parameters correctly.}

\kw{Add population figure?}

>>>>

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GW150914_reprojection.pdf}
\caption{Reprojecting the posterior in evolutionary parameter space of GW150914 to observable space.
The blue contour is the posterior reprojected using the samples in the evolutionary parameter space.
The orange contour is the posterior samples from LVK that have corresponding samples in the evolutionary parameter space.
The green contour is the posterior plotted using all of LVK posterior samples.
}
\label{fig:GW150914_reprojection}
\end{figure}
We can see the reprojected posterior agrees very well with the original posterior in fig.\ref{fig:GW150914_reprojection}.

@@

\begin{figure}
\includegraphics[width=0.49\textwidth]{static/GWTC3_alpha_mass.pdf}
\caption{This figure is ugly as fucked now. Let's change it in later iteration}
\label{fig:GWTC3_alpha_mass}
\end{figure}

\kw{Talk about implication on single event posterior.}
The most important point in this paper is illustrated in figure \ref{fig:GW150914_m1_m2_alpha}.
We can see the posterior samples in $M_1-M_2$ space are spatially correlated with $\alpha$,
this means if we fixed the value of $\alpha$ instead of allowing it to jointly vary with all other parameters,
we would miss the samples that do not match the chosen value of $\alpha$.
By folding in the hyper-parameters into the root-finding algorithm,
we can capture the correlation between 
\kw{Dartboard comparsion} Comparing our result with

\kw{Discuss implication in population.}
To illustrate the potential benefit of our method in the population, we perform the same analysis for most of the events in GWTC3.

Plotted in figure \ref{fig:GWTC3_alpha_mass} is the constraint of $f_{\rm acc}$ for all the events included in the analysis sorted by the median of their inferred primary mass in the observable space.
Note that some events on the extreme of the mass spectrum did not pass the KL divergence test we proposed in section \ref{sec:method}.
\kw{Double check}On the low mass end, the events are more subjected to random fluctuation because natal kick is less modulated by fallback in lighter system, so the reprojected 
On the high mass end, \texttt{COSMIC} struggles to produce events in the pair instability supernova mass gap,
so the posterior in the evolutionary parameter space only correspond part of the posterior in the observable space, therefore events beyond the PISN mass gap has higher KL divergence.

The point of figure \ref{fig:GWTC3_alpha_mass} is to show this method could reveal the correlation between the primary mass in the BBH and the common envelope efficiency.
A careful treatment of each event in the catalog and discussion related the physical implication of figure \ref{fig:GWTC3_alpha_mass} is beyond the scope of this paper,
therefore we defer a detail study of the physics related to the population of GW events in the future.
